From Reversible Programs to \\ Univalent Universes and Back

### 2017-05-11 upi.tex
abstract

\begin{abstract}
  We establish a close connection between a reversible programming language
  based on type isomorphisms and a univalent (in the sense of Homotopy Type
  Theory) universe. The correspondence relates combinators witnessing type
  isomorphisms in the programming language to paths in the univalent universe,
  and combinator optimizations in the programming language to 2-paths in the
  univalent universe. The result provides a simple computational interpretation
  of paths, 2-paths, and univalence in terms of familiar programming constructs.
\end{abstract}

>>>>

\begin{abstract}
  We establish a close connection between a reversible programming language
  based on type isomorphisms and a formally presented univalent universe. The
  correspondence relates combinators witnessing type isomorphisms in the
  programming language to paths in the univalent universe, and combinator
  optimizations in the programming language to 2-paths in the univalent
  universe. The result suggests a simple computational interpretation of paths
  and of univalence in terms of familiar programming constructs whenever the
  universe in question is computable.
\end{abstract}
